Milestone 2: Feature Selection - Subclassing, Malahanobis

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection/feature_selection_cem_mahalanobis.Rmd
Tidying things up for clarity

---
title: "Milestone 2: Feature Selection - Nearest Neighbors, Mahalanobis"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

results_file_name <- 'feature_selection_nn_mahalanobis.RData' 
results_file_path <- file.path('data', results_file_name)
```

@@

```{r fs1, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs1)
```

```{r fs1_noreplace, error=TRUE}
res_fs1_noreplace <- list()
for (bt in names(bts)){
  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs1_noreplace)
```

@@

```{r fs2, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs2)
```

```{r fs2_noreplace, error=TRUE}
res_fs2_noreplace <- list()
for (bt in names(bts)){
  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs2_noreplace)
```

@@

```{r fs3, error=TRUE}
res_fs3 <- list()
for (bt in names(bts)){
  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs3)
```

```{r fs3_noreplace, error=TRUE}
res_fs3_noreplace <- list()
for (bt in names(bts)){
  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs3_noreplace)
```

@@

```{r fs4, error=TRUE}
res_fs4 <- list()
for (bt in names(bts)){
  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs4)
```

```{r fs4_noreplace, error=TRUE}
res_fs4_noreplace <- list()
for (bt in names(bts)){
  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs4_noreplace)
```

@@

```{r fs5, error=TRUE}
res_fs5 <- list()
for (bt in names(bts)){
  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs5)
```

```{r fs5_noreplace, error=TRUE}
res_fs5_noreplace <- list()
for (bt in names(bts)){
  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs5_noreplace)
```

@@

```{r fs6, error=TRUE}
res_fs6 <- list()
for (bt in names(bts)){
  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs6)
```

```{r fs6_noreplace, error=TRUE}
res_fs6_noreplace <- list()
for (bt in names(bts)){
  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs6_noreplace)
```

@@

```{r fs7, error=TRUE}
res_fs7 <- list()
for (bt in names(bts)){
  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs7)
```

```{r fs7_noreplace, error=TRUE}
res_fs7_noreplace <- list()
for (bt in names(bts)){
  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs7_noreplace)
```

# FS 1 Interactions

Feature selection on only performance metrics, but including interaction terms.

```{r fs1_int, error=TRUE}
res_fs1_int <- list()
for (bt in names(bts)){
  res_fs1_int[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, workers = 10, add_interactions=TRUE,
                                      replace=TRUE, distance = 'mahalanobis')
}
save.image(results_file_path)
print(res_fs1_int)
```

>>>>

---
title: "Milestone 2: Feature Selection - CEM, Mahalanobis"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

results_file_name <- 'feature_selection_cem_mahalanobis.RData' 
results_file_path <- file.path('data', results_file_name)
```

@@

```{r fs1, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, k2k= TRUE, workers = 10, 
                                      method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs1)
```

```{r fs1_noreplace, error=TRUE}
res_fs1_noreplace <- list()
for (bt in names(bts)){
  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, k2k= FALSE, workers = 10, 
                                                method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs1_noreplace)
```

@@

```{r fs2, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, k2k= TRUE, workers = 10, 
                                      method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs2)
```

```{r fs2_noreplace, error=TRUE}
res_fs2_noreplace <- list()
for (bt in names(bts)){
  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, k2k= FALSE, workers = 10, 
                                                method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs2_noreplace)
```

@@

```{r fs3, error=TRUE}
res_fs3 <- list()
for (bt in names(bts)){
  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, k2k= TRUE, workers = 10, 
                                      method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs3)
```

```{r fs3_noreplace, error=TRUE}
res_fs3_noreplace <- list()
for (bt in names(bts)){
  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, k2k= FALSE, workers = 10, 
                                                method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs3_noreplace)
```

@@

```{r fs4, error=TRUE}
res_fs4 <- list()
for (bt in names(bts)){
  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, k2k= TRUE, workers = 10, 
                                      method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs4)
```

```{r fs4_noreplace, error=TRUE}
res_fs4_noreplace <- list()
for (bt in names(bts)){
  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, k2k= FALSE, workers = 10, 
                                                method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs4_noreplace)
```

@@

```{r fs5, error=TRUE}
res_fs5 <- list()
for (bt in names(bts)){
  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, k2k= TRUE, workers = 10, 
                                      method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs5)
```

```{r fs5_noreplace, error=TRUE}
res_fs5_noreplace <- list()
for (bt in names(bts)){
  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, k2k= FALSE, workers = 10, 
                                                method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs5_noreplace)
```

@@

```{r fs6, error=TRUE}
res_fs6 <- list()
for (bt in names(bts)){
  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, k2k= TRUE, workers = 10, 
                                      method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs6)
```

```{r fs6_noreplace, error=TRUE}
res_fs6_noreplace <- list()
for (bt in names(bts)){
  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, k2k= FALSE, workers = 10, 
                                                method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs6_noreplace)
```

@@

```{r fs7, error=TRUE}
res_fs7 <- list()
for (bt in names(bts)){
  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, k2k= TRUE, workers = 10, 
                                      method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs7)
```

```{r fs7_noreplace, error=TRUE}
res_fs7_noreplace <- list()
for (bt in names(bts)){
  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, k2k= FALSE, workers = 10, 
                                                method = 'cem', distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs7_noreplace)
```

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection/feature_selection_nn_probit_linear_f.Rmd
Tidying things up for clarity

---
title: "Milestone 2: Feature Selection - Nearest Neighbors, GAM Logit"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

**Matching Algorithm Tested**: Nearest-neighbors with GAM logit distance metric

@@

results_file_name <- 'feature_selection_nn_gam_logit.RData' 
results_file_path <- file.path('data', results_file_name)
```

@@

```{r fs1, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs1)
```

```{r fs1_noreplace, error=TRUE}
res_fs1_noreplace <- list()
for (bt in names(bts)){
  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs1_noreplace)
```

@@

```{r fs2, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs2)
```

```{r fs2_noreplace, error=TRUE}
res_fs2_noreplace <- list()
for (bt in names(bts)){
  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs2_noreplace)
```

@@

```{r fs3, error=TRUE}
res_fs3 <- list()
for (bt in names(bts)){
  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs3)
```

```{r fs3_noreplace, error=TRUE}
res_fs3_noreplace <- list()
for (bt in names(bts)){
  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs3_noreplace)
```

@@

```{r fs4, error=TRUE}
res_fs4 <- list()
for (bt in names(bts)){
  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs4)
```

```{r fs4_noreplace, error=TRUE}
res_fs4_noreplace <- list()
for (bt in names(bts)){
  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs4_noreplace)
```

@@

```{r fs5, error=TRUE}
res_fs5 <- list()
for (bt in names(bts)){
  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs5)
```

```{r fs5_noreplace, error=TRUE}
res_fs5_noreplace <- list()
for (bt in names(bts)){
  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs5_noreplace)
```

@@

```{r fs6, error=TRUE}
res_fs6 <- list()
for (bt in names(bts)){
  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs6)
```

```{r fs6_noreplace, error=TRUE}
res_fs6_noreplace <- list()
for (bt in names(bts)){
  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs6_noreplace)
```

@@

```{r fs7, error=TRUE}
res_fs7 <- list()
for (bt in names(bts)){
  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs7)
```

```{r fs7_noreplace, error=TRUE}
res_fs7_noreplace <- list()
for (bt in names(bts)){
  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs7_noreplace)
```

# Serialize and Push to GCP
Save the resultant dataset and bootstrap samples to an R image.

>>>>

---
title: "Milestone 2: Feature Selection - Nearest Neighbors, Probit, with Linear Propensity Score"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

**Matching Algorithm Tested**: Nearest-neighbors with probit distance metric transformed back to linear scale.

@@

results_file_name <- 'feature_selection_nn_probit_linear.RData' 
results_file_path <- file.path('data', results_file_name)
```

@@

```{r fs1, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs1)
```

```{r fs1_noreplace, error=TRUE}
res_fs1_noreplace <- list()
for (bt in names(bts)){
  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs1_noreplace)
```

@@

```{r fs2, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs2)
```

```{r fs2_noreplace, error=TRUE}
res_fs2_noreplace <- list()
for (bt in names(bts)){
  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs2_noreplace)
```

@@

```{r fs3, error=TRUE}
res_fs3 <- list()
for (bt in names(bts)){
  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs3)
```

```{r fs3_noreplace, error=TRUE}
res_fs3_noreplace <- list()
for (bt in names(bts)){
  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs3_noreplace)
```

@@

```{r fs4, error=TRUE}
res_fs4 <- list()
for (bt in names(bts)){
  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs4)
```

```{r fs4_noreplace, error=TRUE}
res_fs4_noreplace <- list()
for (bt in names(bts)){
  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs4_noreplace)
```

@@

```{r fs5, error=TRUE}
res_fs5 <- list()
for (bt in names(bts)){
  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs5)
```

```{r fs5_noreplace, error=TRUE}
res_fs5_noreplace <- list()
for (bt in names(bts)){
  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs5_noreplace)
```

@@

```{r fs6, error=TRUE}
res_fs6 <- list()
for (bt in names(bts)){
  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs6)
```

```{r fs6_noreplace, error=TRUE}
res_fs6_noreplace <- list()
for (bt in names(bts)){
  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs6_noreplace)
```

@@

```{r fs7, error=TRUE}
res_fs7 <- list()
for (bt in names(bts)){
  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs7)
```

```{r fs7_noreplace, error=TRUE}
res_fs7_noreplace <- list()
for (bt in names(bts)){
  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
}
save.image(results_file_path)
print(res_fs7_noreplace)
```

# Serialize and Push to GCP
Save the feature selection results to GCP.

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection/feature_selection_subclass_mahalanobis.Rmd
Tidying things up for clarity

---
title: "Milestone 2: Feature Selection - Subclassing, GAM Logit"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

results_file_name <- 'feature_selection_subclass_gam_logit.RData' 
results_file_path <- file.path('data', results_file_name)
```

@@

```{r fs1, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL,  workers = 10, 
                                      method = "subclass", distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs1)
```

@@

```{r fs2, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL,  workers = 10, method = "subclass", distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs2)
```

@@

```{r fs3, error=TRUE}
res_fs3 <- list()
for (bt in names(bts)){
  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL,  workers = 10, 
                                      method = "subclass", distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs3)
```

@@

```{r fs4, error=TRUE}
res_fs4 <- list()
for (bt in names(bts)){
  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL,  workers = 10, 
                                      method = "subclass", distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs4)
```

@@

```{r fs5, error=TRUE}
res_fs5 <- list()
for (bt in names(bts)){
  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL,  workers = 10, 
                                      method = "subclass", distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs5)
```

@@

```{r fs6, error=TRUE}
res_fs6 <- list()
for (bt in names(bts)){
  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL,  workers = 10, 
                                      method = "subclass", distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs6)
```

@@

```{r fs7, error=TRUE}
res_fs7 <- list()
for (bt in names(bts)){
  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL,  workers = 10,
                                      method = "subclass", distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs7)
```

>>>>

---
title: "Milestone 2: Feature Selection - Subclassing, Malahanobis"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

results_file_name <- 'feature_selection_subclass_mahalanobis.RData' 
results_file_path <- file.path('data', results_file_name)
```

@@

```{r fs1, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL,  workers = 10, 
                                      method = "subclass", distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs1)
```

@@

```{r fs2, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL,  workers = 10, method = "subclass", distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs2)
```

@@

```{r fs3, error=TRUE}
res_fs3 <- list()
for (bt in names(bts)){
  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL,  workers = 10, 
                                      method = "subclass", distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs3)
```

@@

```{r fs4, error=TRUE}
res_fs4 <- list()
for (bt in names(bts)){
  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL,  workers = 10, 
                                      method = "subclass", distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs4)
```

@@

```{r fs5, error=TRUE}
res_fs5 <- list()
for (bt in names(bts)){
  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL,  workers = 10, 
                                      method = "subclass", distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs5)
```

@@

```{r fs6, error=TRUE}
res_fs6 <- list()
for (bt in names(bts)){
  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL,  workers = 10, 
                                      method = "subclass", distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs6)
```

@@

```{r fs7, error=TRUE}
res_fs7 <- list()
for (bt in names(bts)){
  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL,  workers = 10,
                                      method = "subclass", distance = "mahalanobis")
}
save.image(results_file_path)
print(res_fs7)
```
